\documentclass[11pt,a4paper]{article}
\usepackage[margin=2cm]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontawesome}

\hypersetup{colorlinks=true, linkcolor=blue, filecolor=blue, urlcolor=blue}

\begin{document}
\thispagestyle{empty}

\textbf{\LARGE Shakra Shamim} \\
Data Analyst \\
\+91-9919XXXXXX \quad |\quad shakrashamim09@gmail.com \quad |\quad \href{https://linkedin.com/in/shakrashamim}{linkedin.com/in/shakrashamim} \quad |\quad \href{https://github.com/shakrashamim09}{github.com/shakrashamim09}

\section*{Summary}
Data Analyst with a strong foundation in SQL, Python, Excel, and Power BI. Skilled in cleaning, analyzing, and visualizing data to generate insights and support data-driven decision-making. Interested in collaborating on meaningful analytical work in fast-paced environments.

\section*{Skills}
\begin{itemize}[noitemsep]
\item \textbf{Programming \& Querying:} SQL, Python
\item \textbf{Data Visualization Tools:} Advanced MS Excel, Power BI, Tableau
\item \textbf{Analytical Abilities:} Data Cleaning, Exploratory Data Analysis (EDA), Insight Generation, Descriptive Statistics
\end{itemize}

\section*{Experience}
\textbf{Data Analyst Intern} \hfill April 2025 -- June 2025 \\
\textit{Dataview Analytics (Remote)} \quad Tools Used: Excel, SQL, Power BI
\begin{itemize}
\item Processed and standardized a dataset of over 1,00,000 rows from multiple regions to support weekly analytics—enabled business teams to track KPIs across geography and time.
\item Designed smart Excel templates embedded with lookup functions and pivot logic, saving 40\% reporting time across 4 departments.
\item Developed and maintained Power BI dashboards to visualize revenue trends, customer mix, and monthly performance—regularly used by managers and analysts across business units.
\item Collaborated with 4 analysts and 2 senior managers to define and validate 6 KPIs, improving report reliability and strategic alignment.
\end{itemize}

\section*{Projects}
\textbf{Customer Churn Analysis | Python} \hfill March 2025 -- April 2025
\begin{itemize}
\item Analyzed behavior of 7,043 telecom customers to identify churn patterns based on tenure, contract type, and monthly charges.
\item Engineered new features including contract type buckets and tenure bands to improve segmentation and insights.
\item Generated 11 visualizations (histograms, box plots, heatmaps) to highlight churn-prone segments.
\item Revealed that 38\% of churned users were on monthly contracts with less than 3-month tenure—suggested early engagement strategies.
\end{itemize}

\textbf{Sales Dashboard for Regional Performance | SQL, Power BI} \hfill February 2025 -- March 2025
\begin{itemize}
\item Queried and joined 3 sales-related tables covering over 25,000 rows across 12 months and 5 regions using optimized SQL joins to create consistent, analysis-ready datasets.
\item Built 10 dynamic measures and KPIs in Power BI to track regional sales, return trends, and product performance.
\item Designed multipage dashboards with slicers and filters, helping stakeholders drill down by region, product category, and time.
\item Detected a 14\% sales drop post-festival in the South region. Later, the insight was used for a marketing recovery plan.
\end{itemize}

\section*{Awards \& Certifications}
\begin{itemize}
\item \textbf{Google Data Analytics Certificate -- Coursera (2024):} Completed 8 practical case studies involving SQL, data cleaning, dashboards, and presentations.
\item \textbf{Top 5\% in SQL Hackerrank Challenge -- 2024:} Ranked among top 150 out of more than 3,000 participants for advanced SQL problem-solving.
\item \textbf{Best Final Year Project -- 2025, Marwari College:} Built a Power BI dashboard analyzing academic performance across 6 departments over 3 years.
\end{itemize}

\section*{Education}
\textbf{B.Sc. Information Technology} \hfill Graduated: 2025 \\
Marwari College, Ranchi

\end{document}